### 2016-03-09 Standardmodel.tex
remark about Wilson loop (still undone)

In comparison to the Dirac-Lagrangian \ref{eq:DiracLagrangian} the partial derivative is replaced with the gauge covariant derivative $D^\mu = \partial^\mu + igT^aG^{a\mu}$ and the gauge invariant kinetic term for the gauge fields is added. This comprises the field strenth-tensor $F^{a\mu\nu}$ which is in its matrix valued form defined by $F^{\mu\nu} = F^{a\mu\nu}T^a = \frac{1}{ig}[D^\mu,D^\nu]$.\\

@@

where for each field the corresponding representation (fundamental or trivial) of the gauge group is to be inserted (see table \ref{tab:SMfieldcontent}). The hyper charge operator $\hat{Y}$ gives the eigenvalue of the hypercharge of the field it is applied to. These can be taken from table \ref{tab:SMfieldcontent}.

>>>>

In comparison to the Dirac-Lagrangian \ref{eq:DiracLagrangian} the partial derivative is replaced with the gauge covariant derivative $D^\mu = \partial^\mu + igT^aG^{a\mu}$ and the gauge invariant kinetic term for the gauge fields is added. This comprises the field strenth-tensor $F^{a\mu\nu}$ which is in its matrix valued form defined by $F^{\mu\nu} = F^{a\mu\nu}T^a = \frac{1}{ig}[D^\mu,D^\nu]$. In fact one has little choice for kinetic terms of the gauge fields for thy must be gauge invariant and therefore be functions of the Wilson loop \cite{Peskin}...\\

@@

where for each field the corresponding representation (fundamental or trivial) of the gauge group is to be inserted (see table \ref{tab:SMfieldcontent}). The hyper charge operator $\hat{Y}$ gives the eigenvalue of the hypercharge of the field it is applied to. These can be found in table \ref{tab:SMfieldcontent}.
